---
title: "R Notebook"
output: html_notebook
---

# Q1
```{r}
weather_forecast_for_next_3_days <- list(
                                        "Thursday" = list(Temp = "15", ChanceOfRain = "11%", WindSpeed = "6"),
                                        "Friday" = list(Temp = "18", ChanceOfRain = "43%", WindSpeed = "7"),
                                        "Saturday" = list(Temp = "19", ChanceOfRain = "92%", WindSpeed = "13")
                                        )
weather_forecast_for_next_3_days
```

# Q2
## chance of rain tomorrow
```{r}
weather_forecast_for_next_3_days$Thursday$ChanceOfRain
```

## wind speed on the day after tomorrow
```{r}
weather_forecast_for_next_3_days$Friday$WindSpeed
```

## tempreture tomorrow
```{r}
weather_forecast_for_next_3_days$Thursday$Temp
```

# Q3 Find a 14 day forecast online and create a matrix of the forecasts for temperature, where each week is one row and columns correspond to days.

# You will want to give a name to the matrix you create.
```{r}
# tempretures for the next 14 days
c(20,18,19,20,18,17,17,18,19,19,18,18,18,17)

# creating the matrix and naming the rows and columns
temp_forecast_for_14_days <- matrix(c(20,18,19,20,18,17,17,18,19,19,18,18,18,17), nrow = 2, ncol = 7, byrow = T)
colnames(temp_forecast_for_14_days) <- c("Thursday", "Friday", "Saturday", "Sunday","Monday", "Tuesday", "Wednesday")
rownames(temp_forecast_for_14_days) <- c("Week 1", "Week 2")
temp_forecast_for_14_days
```

# Q4
## From the matrix you just made select:
### The third day of the second week
```{r}
temp_forecast_for_14_days[2,3]
```

#### The whole second week
```{r}
temp_forecast_for_14_days[2,]
```

##### The first, third and fifth days in both weeks.
```{r}
temp_forecast_for_14_days[c(1,2), c(1,3,5)]
```
  
# Q5 
# Write a function that pre-appends “The answer is:” to any character input, while for numeric input, it either just returns the number for numbers less than 10, or divides the number by 10 for numbers greater than 10. For anything else return “Invalid input”.

```{r}
is_value_greater_less_than_10 <- function(x){
if (x < 10){
    print(x)
} else if (x > 10){
  ans <- x / 10
    print(ans)
} else {
    print("The answer is", x)
} 
  print("invalid input")
}
is_value_greater_less_than_10(66)
```

